---
title: "Brock_Rowley_Lab2"
author: "Brock Rowley"
date: "4/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(httr)
#install.packages("repurrrsive")
library(repurrrsive)
```

# PART A
## Run the code below to load the following data set:
```{r runthiscode}
file <- "https://github.com/datalorax/esvis/raw/master/data/benchmarks.rda"
load(url(file))
#head(benchmarks)
```

## Recode season to wave with the following code:
```{r recode}
benchmarks <- benchmarks %>%
    as_tibble() %>%
    mutate(wave = case_when(season == "Fall" ~ 0,
                            season == "Winter" ~ 1,
                            TRUE ~ 2))
```

## 1. Fit a model of the form lm(math ~ wave) for each student.
```{r lmmodelfit}
# Split benchmarks by sid:
stud_split <- split(benchmarks, benchmarks$sid)
# str(stud_split)

# Fit a model:
model <- map(stud_split, ~lm(math ~ wave, data = .x))
# str(model)

# map: loops through each stud_split to fit lm(math ~ wave) for each student.

# Print first three models
# model[1:3]
```

## 2. Plot the distribution of slopes. Annotate the plot with a vertical line for the mean.
```{r plotslopes, warning = FALSE, message = FALSE}
#coef extracts coefficients for any model

coefs <- map(model, ~coef(.x))
# map(data, ~function(placeholder for each iteration))
# This would also work: map(mods, coef)

# Extract the slopes:
slopes <- map_dbl(coefs, ("wave"))
# str(slopes)
# This returns a dbl vector as it loops through each list in coefs and extracts "wave".

# Plot slopes, first create a tibble: 
relation <- tibble(student = names(slopes),
                   slope = slopes)

ggplot(relation, aes(slope)) +
  geom_histogram(fill = "cornflowerblue",
                 color = "white") +
  geom_vline(aes(xintercept = mean(slope, na.rm = TRUE)))
```

# PART B: STAR WARS
## 1. Use the sw_films. Identify how many characters were represented in each film.
```{r charactersperfilm}
length(sw_films)

# Try to extract $characters from one film in sw_films
sw_films[[1]]$characters
length(sw_films[[1]]$characters)

# Using map_dbl and map_chr
chr_count <- map_dbl(sw_films, ~length(.x$characters))
chr_names <- map_chr(sw_films, "title")

# Making a tibble: tibble(ColName = object)
tibble(Film = chr_names,
              Characters = chr_count)
```

## 2 Use sw_species to:  
### (a) identify species that have known hair colors  
### (b) identify what those hair colors are.
```{r identifyhaircolors}
# str(sw_species)
# Map to extract hair color and assign to object.
hc <- map_chr(sw_species, "hair_colors")
# str(hc)

# Map to extract species and assign to object.
species <- map_chr(sw_species, "name")
# str(species)

# Create a tibble with both hair color and species name, filter out those with unknown hair color.
tbl <- tibble(Species = species,
               `Hair Colors` = hc) %>%
  filter(`Hair Colors` != "n/a" &
          `Hair Colors` != "none" & 
          `Hair Colors` != "unknown")
tbl
```

# PART C: Some "basic" API calls
```{r abilities_pokeapi}
ability1 <- GET("https://pokeapi.co/api/v2/ability/1") %>%
  content("parsed")
# str(ability1)
length(ability1$pokemon)
ability1$name
length(ability1$pokemon)
```

## 1 Use {purrr} to write an API call to obtain data on the first five abilities. Parse the JSON data to a list.
```{r APIonfirstfive}
abilities <- paste0("https://pokeapi.co/api/v2/ability/", 1:5)
abs <- map(abilities, ~GET(.x) %>%
                content("parsed"))
# str(abs)
```

## 2 Use the parsed data to create a data frame that has the given ability, and the number of pokemon with that ability.
```{r abilitynumber}
ability <- map_chr(abs, "name")
pokemon_number <- map_dbl(abs, ~length(.x$pokemon))

tbl2 <- tibble(Ability = ability,
       `Number of Pokemon` = pokemon_number)
tbl2

#Stephanie did it a little different... She first does it for one (like D.A suggests) also, explicitly called str_to_title in the tibble.

# Extract length for 1 list
#length(abs[[1]]$pokemon)

# Convert with map 
# count <- map(abs, list("pokemon")) %>%
  #map_dbl(~length(.x))

# Create a tibble
#tbl3 <- tibble(Ability = str_to_title(ability), 
              #`Number of Pokemon` = count)
#tbl3
```